Learning and comparing functional connectomes between populations

### 2012-12-27 paper.tex
Finish the mutual information paragraph

\subsection{Comparing Network Summary Statistics}

\paragraph{Network integration}
%
To avoid the multiple comparison issue and to capture the network-level
distributed variability, a possible strategy is to perform comparison and
statistical testing at the level of the network, rather than the
individual connection. In particular, Marrelec \emph{et al.}\
\cite{marrelec2008} introduce the use of entropy and mutual information
as a measure of network integration\footnote{See \cite{varoquaux2010c}
for simplified formulas for network integration and mutual information.}.
Gaussian entropy can be seen as a simple metric to generalize correlation
or variance to multiple nodes (see \cite{anderson1958} \S2.5.2 and
\S7.5). Indeed, let us considering 3 nodes: $a$, $b$ and $c$. Their
correlation structure is captured by three correlation coefficients:
$\rho_{ab}$, $\rho_{bc}$ and $\rho_{ac}$.

% Rmk average of correlations will measure the sphericity of the
% distribution

%{{{------ Integration measure -----------------------------------------------
\begin{figure}
\begin{minipage}{.19\linewidth}
    \center\sffamily
    {\small Integration:}

    1.513
\end{minipage}%
\begin{minipage}{.25\linewidth}
    \includegraphics[width=\linewidth]{correlation_ex1.pdf}
\end{minipage}%
\hfill%
\begin{minipage}{.25\linewidth}
    \includegraphics[width=\linewidth]{correlation_ex2.pdf}
\end{minipage}%
\begin{minipage}{.19\linewidth}
    \center\sffamily
    {\small Integration:}

    0.492
\end{minipage}%

\caption{Two different correlation matrix with the same average
correlation, but integration values that strongly differ.
\label{fig:integration}}
\end{figure}
%---------------------------------------------------------------------------}}}

>>>>

\subsection{Comparing network summary statistics}

\paragraph{Network integration}
%
To avoid the multiple comparison issue and to capture the network-level
distributed variability, a possible strategy is to perform comparison and
statistical testing at the level of the network, rather than the
individual connection. In particular, Marrelec \emph{et al.}\
\cite{marrelec2008} introduce the use of entropy and mutual information
as a measure of network integration\footnote{See \cite{varoquaux2010c}
for simplified formulas for network integration and mutual information.}.
Gaussian entropy can be seen as a simple metric to generalize correlation
or variance to multiple nodes (see \cite{anderson1958} \S2.5.2 and
\S7.5). Indeed, let us considering 3 nodes: $a$, $b$ and $c$. Their
correlation structure is captured by three correlation coefficients:
$\rho_{ab}$, $\rho_{bc}$ and $\rho_{ac}$. Summarizing these by their
mean, as it might seem natural, discards the relationship between the
signals, while using the integration tells us how much two signals can be
combined to form the third (see Fig.\,\ref{fig:integration}). Similarly
as Gaussian entropy can be used to measure the integration of a brain
system or network, cross-entropy --or mutual information--
\cite{marrelec2008} measures the amount of cross-talk between two
systems. The functional-connectivity structure, or its representation in
form of a correlation matrix, can thus be characterized via the
integration and cross-talk of some of its subs-systems. This appraoch
gives a simplified representation with a small number of metrics that can
be compared across subjects.

%{{{------ Integration measure -----------------------------------------------
\begin{figure}
\hspace*{2ex}%
\begin{minipage}{.19\linewidth}
    \center\sffamily
    {\small Integration:}

    0.554
\end{minipage}%
\begin{minipage}{.2\linewidth}
    \includegraphics[width=\linewidth]{correlation_ex1.pdf}
\end{minipage}%
\hfill%
\begin{minipage}{.033\linewidth}
    \includegraphics[width=\linewidth]{correlation_cmap.pdf}%
    \llap{\raisebox{.4ex}{\scriptsize\sffamily\bfseries 0}\hspace*{.54ex}}%
    \llap{\raisebox{10.1ex}{\scriptsize\sffamily\bfseries\color{white} 1}%
	    \hspace*{.54ex}}
\end{minipage}%
\hfill%
\begin{minipage}{.2\linewidth}
    \includegraphics[width=\linewidth]{correlation_ex2.pdf}
\end{minipage}%
\begin{minipage}{.19\linewidth}
    \center\sffamily
    {\small Integration:}

    2.422
\end{minipage}%
\hspace*{2ex}%

\caption{Two different correlation matrices with the same average
correlation, but with very different integration values. Indeed, the
matrix on the left was chosen to have represent three signals $a$, $b$
and $c$ as different from each other as possible, given $\rho_{ab} +
\rho_{bc} + \rho{ac} = 1.35$; it thus as a small integration value. On
the opposite, for the matrix on the right, signal $b$ can almost be fully
recovered by combining signals $a$ and $c$; the matrix thus has a large
integration value.
\label{fig:integration}}
% Rmq: in this example, in the second figure, the 3 signals are more
% independent, and thus define a wider range of acceptable signal.
\end{figure}
%---------------------------------------------------------------------------}}}
